A biometric analysis of infant mortality and temperature, northern Sweden 1895-1950

### 2022-01-09 paper.Rmd
rearranging

---
title: "A biometric analysis of infant mortality and temperature, northern Sweden 1895-1950"
author: "Göran Broström and Tommy Bengtsson"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: yes
    number_sections: yes
    toc: no
    toc_depth: 2
  bookdown::word_document2:
    toc: no
    toc_depth: 2
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
citation_package: natbib
classoption: titlepage
bibliography: bio.bib
titlepage: yes
biblio-style: apalike
documentclass: article
fontsize: 11pt
header-includes:
- \usepackage[utf8]{inputenc}
- \usepackage{graphicx}
abstract: "The effect of extreme temperatures on infant mortality in the Umeå region 1895-1950 is studied in a biometric analysis setting."
---

@@

# The Bourgeouis-Pichat model and the approximation

@@

However, we show that the BP transformation is well approximated by a model where the 
*cumulative hazards function* is linear instead, that is, an *exponential distribution*,
easy to use in standard survival regression analysis, often allowing for massive data reduction
through the statistical *sufficency pinciple*.

@@

## Add weather data

@@

In accordance with the Bourgeouis-Pichat ideas, we group the analyses into two parts, 
*neonatal* (first 28 days) och *postneonatal* mortality (days 29--365).

>>>>

---
title: "A biometric analysis of infant mortality and temperature, northern Sweden 1895-1950"
author: "Göran Broström and Tommy Bengtsson"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: yes
    number_sections: yes
    toc: yes
    toc_depth: 3
  bookdown::word_document2:
    toc: no
    toc_depth: 2
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
citation_package: natbib
classoption: titlepage
bibliography: bio.bib
titlepage: yes
biblio-style: apalike
documentclass: article
fontsize: 11pt
header-includes:
- \usepackage[utf8]{inputenc}
- \usepackage{graphicx}
abstract: "The effect of extreme temperatures on infant mortality in the Umeå region 1895-1950 is studied in a biometric analysis setting."
---

@@

# The Bourgeouis-Pichat model

@@

However, we show that the BP transformation is well approximated by a model where the 
*cumulative hazards function* is linear instead, that is, an *exponential distribution*,
easy to use in standard survival regression analysis, often allowing for massive data reduction
through the statistical *sufficency principle*.

@@

### Putting it together

## Infant data

In the previous chapter we introduced data on infant mortality from the Umeå-Skellefteå
region 1895--1950, and here we introduce covariates of interest in the forthcoming  analyses, 
see Table

## Weather data

@@

In accordance with the ideas of Bourgeouis-Pichat, we group the analyses into two parts, 
*neonatal* (first 28 days) och *postneonatal* mortality (days 29--365).
